Template for indicator documentation

### 2023-09-11 DRAFT_functional_plant_indicators_natopen.Rmd
Update DRAFT_functional_plant_indicators_natopen.Rmd
backing up the last changes (small layout changes)

ANO data: ANO.sp contains the species data, ANO.geo contains site data
```{r, echo = F}
# Add data from cache
ANO.sp<-readRDS(paste0(here::here(),"/data/cache/ANO.sp.RDS"))
ANO.geo<-readRDS(paste0(here::here(),"/data/cache/ANO.geo.RDS"))
```

GRUK data: GRUK.species contains the species data, GRUK.variable contains site data, GRUK2021.condition contains a field-based condition assessment from the 2021 season
```{r, echo = F}
# Add data from cache
GRUK.variables<-readRDS(paste0(here::here(),"/data/cache/GRUK.variables.RDS"))
GRUK.species<-readRDS(paste0(here::here(),"/data/cache/GRUK.species.RDS"))
GRUK2021.condition<-readRDS(paste0(here::here(),"/data/cache/GRUK2021.condition.RDS"))
```

Plant indicators from Tyler et al. (2021) and Grime (1974)
```{r, echo = F}
## data from cache
ind.Tyler<-readRDS(paste0(here::here(),"/data/cache/ind.Tyler.RDS"))
ind.Grime<-readRDS(paste0(here::here(),"/data/cache/ind.Grime.RDS"))
```

Generalized species lists (reference communities): natopen_NiN_ref contains the reference species lists, natopen_NiN_ref_spInfo contains additional taxonomic information for each species
```{r, echo = F}
# data from cache
natopen_NiN_ref<-readRDS(paste0(here::here(),"/data/cache/natopen_NiN_ref.RDS"))
natopen_NiN_ref_spInfo<-readRDS(paste0(here::here(),"/data/cache/natopen_NiN_ref_spInfo.RDS"))
```

>>>>

ANO data: ANO.sp contains the species data, ANO.geo contains site data.
```{r, echo = F}
# Add data from cache
ANO.sp<-readRDS(paste0(here::here(),"/data/cache/ANO.sp.RDS"))
ANO.geo<-readRDS(paste0(here::here(),"/data/cache/ANO.geo.RDS"))
```

GRUK data: GRUK.species contains the species data, GRUK.variable contains site data, GRUK2021.condition contains a field-based condition assessment from the 2021 season.
```{r, echo = F}
# Add data from cache
GRUK.variables<-readRDS(paste0(here::here(),"/data/cache/GRUK.variables.RDS"))
GRUK.species<-readRDS(paste0(here::here(),"/data/cache/GRUK.species.RDS"))
GRUK2021.condition<-readRDS(paste0(here::here(),"/data/cache/GRUK2021.condition.RDS"))
```

Plant indicators from Tyler et al. (2021) and Grime (1974) are saved as ind.Tyler and ind.Grime.
```{r, echo = F}
## data from cache
ind.Tyler<-readRDS(paste0(here::here(),"/data/cache/ind.Tyler.RDS"))
ind.Grime<-readRDS(paste0(here::here(),"/data/cache/ind.Grime.RDS"))
```

Generalized species lists (reference communities): natopen_NiN_ref contains the reference species lists, natopen_NiN_ref_spInfo contains additional taxonomic information for each species.
```{r, echo = F}
# data from cache
natopen_NiN_ref<-readRDS(paste0(here::here(),"/data/cache/natopen_NiN_ref.RDS"))
natopen_NiN_ref_spInfo<-readRDS(paste0(here::here(),"/data/cache/natopen_NiN_ref_spInfo.RDS"))
```
